Big Brother Is Watching

### 2015-11-05 manuscript.tex
added cropped figure

\section{Abstract}
\label{sec:abstract}

@@

\indent \indent The two contingencies that we must account for are the fuel penalty applied when drones make sharp turns, and the possibility that drones may be grounded for repairs. In order to ensure that every location is periodically observed without reprogramming the drones, the drones must all follow the same path and be equally spaced. The path that accomplishes this and minimizes the total number of turns is similar to the one shown in Figure \ref{path}.

@@

    \centering]{{\includegraphics[width=7cm]{figures/optimal_path.pdf} }}%

@@

\newline\indent In our case Manhattan is modeled as being $30\times 250$ blocks. The similar path for this layout has 60 turns and a total path length of 7500 blocks ($\sim 250$ miles). If the speed of each drone is 30 mph then each drone can fly 3000 blocks before having to refuel if we do not account for turning penalties. Since we were not given a specific parameter for drone refueling rates, need to create a flexible model that describes the refueling rates effects on the number of drones required. 

@@

\newline\indent If the drones are equally spaced, then the distance between them in blocks is simply $L/n_{c}$ where $L$ is the total path length (7500 blocks). By setting the maximum time interval $t$ to 15 min in Equation \ref{max time interval} we can solve for the minimum number of drones required given that the drones travel at a rate $R = 10$ blocks/minute (30mph). Our representation of the city requires $n_{c} = 50$ for a maximum unobserved interval of 15 minutes.

@@

\newline\indent Now we account for the possibility that drones can break down and be grounded for repairs. We analyze the effect of at most 30\% becoming unusable. We assume that if a drone fails then the currently operating drones spread out evenly over the entire path to keep visit intervals at a minimum. Figure \ref{failed} shows the maximum unobserved time interval given drone failings ranging from 0 to 30\%. If 30\% fail then the maximum interval is increased to 21.12 minutes. 

@@

    \centering]{{\includegraphics[width=7cm]{figures/failed_drones.pdf} }}%
    \caption{Drone failings effect on maximum visit interval}

@@

\indent If this plan is implemented then the total number of drones that the city needs to adequately observe all areas is described by Equation \ref{totaldrones}. The worst case would be if refuel times were long and it was mandatory to keep all visit intervals within 15 min. This would require 50 drones to be deployed at all times, 50 should be readily available to deploy when operating drones run out of fuel, and 15 should be readily available to replace any broken drones. This gives us a total of 115 drones. This solution yields a density of 6.13 drones per square mile. The best case scenario would take the refuel times to be negligible and a more flexible tolerance for maximum visit intervals. This case would not require any backup drones for refueling or failures and the resulting an optimal value of 50 total drones (2.67 drones per square mile). The true solution will therefore lie in the range of 50 - 115 drones and depend on the real constraints of the situation subject to the methods we have developed.

>>>>

\section{Abstract}
\label{sec:abstract}
Several models were developed to facilitate the perpetual surveillance of Gotham City using . These models account

@@

The two contingencies that we must account for are the fuel penalty applied when drones make sharp turns, and the possibility that drones may be grounded for repairs. In order to ensure that every location is periodically observed without reprogramming the drones, the drones must all follow the same path and be equally spaced. The path that accomplishes this and minimizes the total number of turns is similar to the one shown in Figure \ref{path}.

@@

    \centering{{\includegraphics[width=7cm]{figures/optimal_path.pdf} }}

@@

\newline In our case Manhattan is modeled as being $30\times 250$ blocks. The similar path for this layout has 60 turns and a total path length of 7500 blocks ($\sim 250$ miles). If the speed of each drone is 30 mph then each drone can fly 3000 blocks before having to refuel if we do not account for turning penalties. Since we were not given a specific parameter for drone refueling rates, need to create a flexible model that describes the refueling rates effects on the number of drones required. 

@@

\newline If the drones are equally spaced, then the distance between them in blocks is simply $L/n_{c}$ where $L$ is the total path length (7500 blocks). By setting the maximum time interval $t$ to 15 min in Equation \ref{max time interval} we can solve for the minimum number of drones required given that the drones travel at a rate $R = 10$ blocks/minute (30mph). Our representation of the city requires $n_{c} = 50$ for a maximum unobserved interval of 15 minutes.

@@

\newline Now we account for the possibility that drones can break down and be grounded for repairs. We analyze the effect of at most 30\% becoming unusable. We assume that if a drone fails then the currently operating drones spread out evenly over the entire path to keep visit intervals at a minimum. Figure \ref{failed} shows the maximum unobserved time interval given drone failings ranging from 0 to 30\%. If 30\% fail then the maximum interval is increased to 21.12 minutes. 

@@

    \centering{{\includegraphics[width=7cm]{figures/failed_drones-crop.pdf} }}
    \caption{Drone failure effects on maximum visit interval}

@@

If this plan is implemented then the total number of drones that the city needs to adequately observe all areas is described by Equation \ref{totaldrones}. The worst case would be if refuel times were long and it was mandatory to keep all visit intervals within 15 min. This would require 50 drones to be deployed at all times, 50 should be readily available to deploy when operating drones run out of fuel, and 15 should be readily available to replace any broken drones. This gives us a total of 115 drones. This solution yields a density of 6.13 drones per square mile. The best case scenario would take the refuel times to be negligible and a more flexible tolerance for maximum visit intervals. This case would not require any backup drones for refueling or failures and the resulting an optimal value of 50 total drones (2.67 drones per square mile). The true solution will therefore lie in the range of 50 - 115 drones and depend on the real constraints of the situation subject to the methods we have developed.
